---
title: "Loading PeakFQR Shiny App"
format: html
editor: visual
---

## Data Sources:
- USGS National Water Information System (NWIS) PeakFQR data: https://nwis.waterdata.usgs.gov/usa/nwis/peakfq 
- USGS Gauge Data

```{r}

library(tidyverse)
library(janitor)
library(here)
library(dplyr)
library(ggplot2)
library(tidyr)
library(kableExtra)
```

## Peak FQR Data

### Loading Necessary Packags 
```{r}
#COMMENTING OUT ONCE RUN
#NOTE: had to install fortran using the following code to run this
  #Step 1: curl -L https://mac.r-project.org/tools/gfortran-12.2-universal.pkg -o ~/gfortran-12.2-universal.pkg
  #Step 2: sudo installer -pkg ~/gfortran-12.2-universal.pkg -target /


#Install Packages from USGS Source
# install.packages("remotes")
# remotes::install_gitlab("water/peakfqr",
#                         host = "code.usgs.gov",
#                         dependencies = TRUE,
#                         INSTALL_opts = "--no-multiarch",
#                         build_opts = c("--no-resave-data", "--no-manual"))

```

### Run Shiny App

Run this code to load up a Shiny app to query data on flow exceedences
-   Site: enter site number from USGS (ex. 11389500)
-   Skew Option: click on box and select station
-   Urban + Regulated Peaks: select these as allowed
-   This Analysis: for the initial analysis used 0.6667 and 0.5 

```{r}
#Run to Open the Shiny App
library(peakfq)
peakfq_app()
```

## Gauge Data 

### Loading Necessary Packages 

```{r}
# Check version
library(dataRetrieval)
packageVersion("dataRetrieval")

```


### Reading in Gauge Data for Single Site

```{r}

#Using Older Version 
#Issue with dataRetrieval, sort out later
polusa <- readNWISdv(
  siteNumbers = "11389500",     # your site number here
  parameterCd = "00060",        # discharge, cfs 
  startDate   = "1941-01-01",   # or whenever you want to start
  endDate     = "2025-12-31"
)

#Clean Column Names 
polusa_clean <- renameNWISColumns(polusa) |>
  clean_names() |>
  rename(dis_cfs = flow) |>
  mutate(dis_m3s = dis_cfs * 0.0283168) 
  
```

### Select Dates that Match Exceedence Values

```{r}
#Using Exceedences From Shiny App, Finding Years that Match 
#Simplified to 3 significant figures, otherwise had no matches 

#Exceedance Probability of 0.6667
q15_exceedences <- polusa_clean |>
  filter(dis_cfs == 37600)

#Exceedance Probability of 0.5
q_2_exceedences <- polusa_clean |>
  filter(dis_cfs == 40500)

#Create Table for Exceedance Years 
kable(q15_exceedences) |>
  kable_styling(font_size = 20)
kable(q_2_exceedences)|>
  kable_styling(font_size = 20)

```
